New_Data_Coherence

### 2019-08-27 Analysis/Coherence_Calculations_New.Rmd
wip to make release ready

```{r}
require(msigdbr)
require(dplyr)
require(readr)
source("./functions/GeneSample.R")
require(biomaRt)

@@

```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1,
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)

```{r}
#Read in edges generated from Connectivity_Comparison_*.Rmd

disease_overall_string = readRDS("string_edges_new.rds")

disease_overall_string_filt = readRDS("string_filt_edges_new.rds")

disease_overall_biogrid = readRDS("biogrid_edges_new.rds")

#Calculate slopes for all diseases under each category

dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)

>>>>

```{r}
library(msigdbr) # install.packages("msigdbr")
library(dplyr)   # install.packages("dplyr")
library(readr)   # install.packages("readr")
source("./functions/GeneSample.R")
library(biomaRt) # BiocManager::install("biomaRt")
```

@@

```{r}
# #Reading in biogrid data
# 
# links = read_tsv("./data/BIOGRID-ALL-3.5.174.mitab.txt")
# 
# #Select human protein-protein interactions
# 
# links = links %>% filter(`Taxid Interactor A` == "taxid:9606" & `Taxid Interactor B` == "taxid:9606")
# 
# #Split based on Biogrid ID system then pull out gene names
# 
# protein1 = lapply(strsplit(links$`Alt IDs Interactor A`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# protein2 = lapply(strsplit(links$`Alt IDs Interactor B`, "locuslink:"), function(x) strsplit(x[2], "\\|")[[1]][1])
# 
# protein1 = unlist(protein1)
# protein2 = unlist(protein2)
# 
# #Place into matrix in form that disease2frame works on
# 
# links = links %>% mutate(protein1 =protein1,
#                              protein2 = protein2) %>% dplyr::select(protein1, protein2)
# 
# links = links %>% dplyr::select(hgnc_symbol_a = protein1,hgnc_symbol_b = protein2)
# 
# 
# dim(links)
```

```{r}
#Read in edges generated from Connectivity_Comparison_*.Rmd
disease_overall_string      <- readRDS("string_edges_new.rds")
disease_overall_string_filt <- readRDS("string_filt_edges_new.rds")
disease_overall_biogrid     <- readRDS("biogrid_edges_new.rds")

#Calculate slopes for all diseases under each category
dis_slopes_string_count = disease_overall_string %>% filter(Internal != 0) %>% filter(Category != "Random") %>% filter(Category != "KEGG") %>%
    group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
    do({
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
      data.frame(Slope= coef(mod)[1])
    }) %>% arrange(Slope) %>% filter(Count>4)
